On the marginal value of swimming in woodland caribou

### 2021-04-12 paper/manuscript.Rmd
P4

`r nevents` 
In total, 12 of 29 collared female caribou swam between islands in the Fogo
Island archipelago. Of the caribou that swam, caribou swam on average
approximately `r neventidMean` (range = `r neventidMin`-`r neventidMax`) times
per year and remained on each island for approximately `r dur` (range = 
`r durMin`-`r durMax`) days before swimming again. Based on GPS data to infer
swimming, we separated the population into three apparent groups of individuals:
those that swam regularly between islands (n = 3, every ~`r indMean` days);
those that rarely engaged in swimming events (n = 9, every ~ `r ind2Mean` days);
and those that never swam (n = 17).

>>>>

Swimming behavior was common among GPS radio-collared caribou in the population (n = 29, for collaring
details see Peignier et al. 2019). We identified `r nevents` swimming events over three years (Figure
2). In total, 13 of 29 collared female caribou swam among islands (Figure 2). Of the caribou that
swam, caribou swam on average approximately `r neventidMean` (range = `r neventidMin`-`r neventidMax`)
times per year and remained on each island for a median of `r dur` (range = 
`r durMin`-`r durMax`) days before swimming again. We found that caribou residency increased
proportionally with the size of the island, such that caribou spent less time on smaller islands and
more time on larger islands, providing preliminary evidence for links between forage limitation and
the marginal value theorem (Figure 2B).

In total, 12 of 29 collared female caribou swam between islands in the Fogo
Island archipelago. Of the caribou that swam, caribou swam on average
approximately `r neventidMean` (range = `r neventidMin`-`r neventidMax`) times
per year and remained on each island for approximately `r dur` (range = 
`r durMin`-`r durMax`) days before swimming again. Based on GPS data to infer
swimming, we separated the population into three apparent groups of individuals:
those that swam regularly between islands (n = 3, every ~`r indMean` days);
those that rarely engaged in swimming events (n = 9, every ~ `r ind2Mean` days);
and those that never swam (n = 17).
